---
title: List Objects
author: Bryce Mecum <mecum@nceas.ucsb.edu>
---

**Task:** Connect to the DataONE production environment, retrieve a few listings of objects.

First, load the `dataone` R package and connect to the production Coordinating Node:

```{r}
library(dataone)
cn <- CNode()
```

`listObjects` accepts a number of optional arguments (see `?listObjects`) such as `count` which controls the number of objects that are returned:

```{r}
listObjects(cn, count = 5)
```

As another example, we can filter to _just_ CSV objects created within a time frame:

```{r}
csvs <- listObjects(cn, 
                    fromDate = "2020-01-01T00:00:00.000Z", 
                    toDate = "2021-01-01T00:00:00.000Z", 
                    formatId = "text/csv", 
                    count = 5)
length(csvs$objectInfo)
```

You can see we received five results like we requested but there are many more available:

```{r}
csvs$.attrs[3]
```
Knowing this, we can use the `start` argument to page through the results:

```{r}
page_two <- listObjects(cn, 
                        fromDate = "2020-01-01T00:00:00.000Z", 
                        toDate = "2021-01-01T00:00:00.000Z", 
                        formatId = "text/csv", 
                        count = 5,
                        start = 5)
```
