---
title: Query for Data
author: Bryce Mecum <mecum@nceas.ucsb.edu>
---

**Task:** Query DataONE for data that's relevant to your interests

DataONE provides a mechanism for one or more query services to be available to clients wanting to query across the federation.

First, load the `dataone` R package:

```{r}
library(dataone)
```

```{r}
cn <- CNode()
listQueryEngines(cn)
```

While the above query services can be accessed directly via the HTTP API, the `dataone` R package provides a `query` function which makes access to the "solr" query engine more user-friendly.

The `list` we pass into `query` matches [Lucene Query Syntax](https://lucene.apache.org/solr/) provided by Solr and lets us make some pretty advanced queries. Let's search for latest versions of metadata records about tundra permafrost and return a list of titles for them:

```{r}
query(cn, list(
  q = "tundra permafrost+AND+formatType:METADATA+AND+-obsoletedBy:*",
  fl = "title",
  rows = 5
))
```

`query` returns a `list` by default but we can change it to a `data.frame` which may make the results more useful:

```{r}
query(cn, list(
  q = "tundra permafrost+AND+formatType:METADATA+AND+-obsoletedBy:*",
  fl = "title",
  rows = 5
), as = "data.frame")
```
